\documentclass[a4paper,12pt]{article}
\usepackage{standalone}
\usepackage{amsmath} % Package for advanced math typesetting
\input{../../sty/setup.sty} % Assuming these files exist and are correctly referenced
\graphicspath{ {../../pictures/IDMA/IDMA2a}} % Assuming a pictures folder has been made and is correctly referenced

% \renewcommand{\thesection}{5.\arabic{section}} % Substitue 5. for any number

% Changes sections from 1.1 to 1.a
\renewcommand{\thesubsection}{\thesection.\alph{subsection}}

\begin{document}
% \includepdf[pages=-]{../../pictures/forside}

\title{Københavns Universitet\\
Introduktion til diskret matematik og algoritmer - Problem set 3}
\input{../../sty/cover.sty} % Assuming this file contains the cover page setup
\input{../../sty/header.sty} % Assuming this file contains the header setup
\maketitle % This command will actually insert the title into the document


\section[Question 1]{Recall that a standard deck of cards has $52$ cards partitioned into four suits (hearts,
spades, clubs, and diamonds) with $13$ ranks each (2-10 plus jack, queen, king, and ace). In this
problem, we assume that you are dealt $5$ cards from a perfectly shuffled deck of cards.}

\subsection[]{What is the probability that you get a flush, i.e., $5$ cards of the same suit but not all in
sequence with respect to rank? (Because five cards of the same suit in sequential rank
would be a straight flush.)}

Først skal vi finde ud af, hvor mange mulige hænder vi kan trække. Siden vi får 5 tilfældige kort uden tilbagelægning, og rækkefølgen ikke betyder noget, kan vi beskrive dette som en binomialkoefficient:
\[ _{52}C_5 = {52 \choose 5} =\]
\[\dfrac{52!}{(52-5)! \cdot 5!} =\]
\[\dfrac{52!}{47! \cdot 5!} = 2.598.960\]
Nu skal vi bestemme mængden af hænder, der laver en flush. Der er 4 forskellige kulører, og vi skal bruge 5 af samme kulør:
\[ _{13}C_5 = {13 \choose 5} = \]
\[ \dfrac{13!}{(13-5)! \cdot 5!} = \]
\[ \dfrac{13!}{8! \cdot 5!} = 1287 \]
Vi skal dog også huske, at der er 4 forskellige kulører, så vi vælger 1 af de 4:
\[ _4C_1 \cdot 1287 = {4 \choose 1} \cdot 1287 = \]
\[ \dfrac{4!}{(4-1)! \cdot 1!} \cdot 1287 = \]
\[ \dfrac{4!}{3!} \cdot 1287 = \]
\[ 4 \cdot 1287 = 5148\]
Der er dog også mulighed for at trække en straight flush, som vi skal trække fra:
\[ _{10}C_1 \cdot _4C1 = {10 \choose 1} \cdot {4 \choose 1} = \]
\[ \dfrac{10!}{(10-1)! \cdot 1!} \cdot \dfrac{4!}{(4-1)! \cdot 1!} = \]
\[ \dfrac{10!}{9!} \cdot \dfrac{4!}{3!} = \]
\[ 10 \cdot 4 = 40\]
Så den samlede mængde af hænder, der laver en flush uden en straight flush, er:
\[ 5148 - 40 = 5108\]
Så sandsynligheden for at trække en flush er:
\[ \dfrac{5108}{2598960} \approx 0.00197\]

\subsection[]{What is the probability that you get a straight, i.e., $5$ 
cards of sequential rank but not all of the same suit? (Because if the latter condition also held, 
we would again have a straight flush.)
}

Vi bestemmer mængden af hænder, der laver en straight. Den laveste straight vi kan lave er $A, 2, 3, 4, 5$, og den højeste er $10, J, Q, K, A$. Fra $A$ til 10 er der 10 måder at lave en straight, hvis vi bare tæller fra og med laveste kort tal af straight'en op til de 10.
\[ _{10}C_1 = {10 \choose 1} = \]
\[ \dfrac{10!}{(10-1)! \cdot 5!} = \]
\[ \dfrac{10!}{9! \cdot 1!} = 10 \]
Vi skal dog også huske, at der er 4 forskellige kulører, så vi vælger 1 af de 4, for hvert af de 5 kort.
\[ _4C_1 \cdot _4C_1 \cdot _4C_1 \cdot _4C_1 \cdot _4C_1 \cdot 10 = {4 \choose 1} \cdot {4 \choose 1} \cdot {4 \choose 1} \cdot {4 \choose 1} \cdot {4 \choose 1} \cdot 10 = \]
\[ \dfrac{4!}{(4-1)! \cdot 1!} \cdot \dfrac{4!}{(4-1)! \cdot 1!} \cdot \dfrac{4!}{(4-1)! \cdot 1!} \cdot \dfrac{4!}{(4-1)! \cdot 1!} \cdot \dfrac{4!}{(4-1)! \cdot 1!} \cdot  10 = \]
\[ \dfrac{4!}{3!} \cdot \dfrac{4!}{3!} \cdot \dfrac{4!}{3!} \cdot \dfrac{4!}{3!} \cdot \dfrac{4!}{3!} \cdot 10 = \]
\[ 4 \cdot 4 \cdot 4 \cdot 4 \cdot 4 \cdot 10 = 10240\]
Der er dog også mulighed for at trække en straight flush, som vi skal trække fra:
\[ 10240 - 40 = 10200\]
Så sandsynligheden for at trække en straight er:
\[ \dfrac{10200}{2598960} \approx 0.00393\]


\section[Question 2]{Prove mathematically that among all numbers on the form $11...100...0$, i.e., numbers
consisting of $m$ ones followed by $n$ zeros for some $m,n \in N^+$ (sometimes notation like $1^m0^n$ is
used to describe text strings constructed in such a way), there is some number that is divisible
by 2025. Hint: Look at all numbers $1^m = 11 ... 1$ and consider what their remainders can be modulo $2025$.}

For at omformulere opgaven, skal vi vise:
\[ \exists m,n \in \N^+ \quad 2025 \mid 1^m0^n\]


\section[Question 3]{Let $a \in R^+$ be any positive real number. Show that for any integer $n \geq 2$ there is a
rational number $\frac{c}{d}, c,d \in \Z, d \leq n$, that approximates $a$ to within error $\frac{1}{dn}$, ie., $|a - \frac{c}{d}| \leq \frac{1}{dn}$.
Hint: Consider the numbers $a, 2a, \dots ,n \cdot a$ and show that one of these numbers is at distance at most $\frac{1}{n}$ from some integer.}



\section[Question 4]{In this problem we focus on relations. Suppose that $A = \{e_0,e_1,\dots,e_5\}$ is a set of
$6$ elements and consider the relation $R$ on $A$ represented by the matrix
\[M_R = 
    \begin{bmatrix}
        0 & 0 & 1 & 0 & 0 & 0 \\
        0 & 0 & 0 & 1 & 0 & 0 \\
        0 & 0 & 0 & 0 & 1 & 0 \\
        0 & 0 & 0 & 0 & 0 & 1 \\
        1 & 0 & 0 & 0 & 0 & 0 \\
        0 & 1 & 0 & 0 & 0 & 0 \\
    \end{bmatrix}
\]
(where element $e_i$ corresponds to the row and column $i+1$).}
\subsection[]{Let us write $S$ to denote the symmetric closure of the relation $R$. 
What is the matrix representation of $S$? Can you explain in words what the relation $S$ is by describing how it can be interpreted?
}

Vi får givet en matrice med relationen $R$ på $A$. Vi ser, at hvis vi repræsenterer matricen som en graf, ender vi med en directed graf, da alle vertices har en directed edge, og ingen af disse går tilbage igen. Grafisk er dette 2 'lukkede' trekanter. Den symetriske closure af en matrix består af dens relation $R$ og dens converse relation $R^{-1}$. For en relation $R$ er dette defineret som: 
\[ R^{-1} = (b,a) : (a,b) \in R\]
som når anvendt på en matrix beskrives som:
\[M_{R^{-1}} = M_{R}^T = 
    \begin{bmatrix}
        0 & 0 & 0 & 0 & 1 & 0 \\
        0 & 0 & 0 & 0 & 0 & 1 \\
        1 & 0 & 0 & 0 & 0 & 0 \\
        0 & 1 & 0 & 0 & 0 & 0 \\
        0 & 0 & 1 & 0 & 0 & 0 \\
        0 & 0 & 0 & 1 & 0 & 0 \\
    \end{bmatrix}
\]

Vi bemærker, at dette er grafisk repræsenteret som de samme 2 lukkede trekanter som før, dog er retningerne af edges'ne omvendt.

\[M_S = M_R \cup M_{R}^T = 
    \begin{bmatrix}
        0 & 0 & 1 & 0 & 0 & 0 \\
        0 & 0 & 0 & 1 & 0 & 0 \\
        0 & 0 & 0 & 0 & 1 & 0 \\
        0 & 0 & 0 & 0 & 0 & 1 \\
        1 & 0 & 0 & 0 & 0 & 0 \\
        0 & 1 & 0 & 0 & 0 & 0 \\
    \end{bmatrix}
    \cup
    \begin{bmatrix}
        0 & 0 & 0 & 0 & 1 & 0 \\
        0 & 0 & 0 & 0 & 0 & 1 \\
        1 & 0 & 0 & 0 & 0 & 0 \\
        0 & 1 & 0 & 0 & 0 & 0 \\
        0 & 0 & 1 & 0 & 0 & 0 \\
        0 & 0 & 0 & 1 & 0 & 0 \\
    \end{bmatrix}
    = 
    \begin{bmatrix}
        0 & 0 & 1 & 0 & 1 & 0 \\
        0 & 0 & 0 & 1 & 0 & 1 \\
        1 & 0 & 0 & 0 & 1 & 0 \\
        0 & 1 & 0 & 0 & 0 & 1 \\
        1 & 0 & 1 & 0 & 0 & 0 \\
        0 & 1 & 0 & 1 & 0 & 0 \\
    \end{bmatrix}
\]

Resultatet er, at de 2 lukkede trekanter nu både har udgående edges fra $M_R$ og $M^T_{R}$. Edges'ne går nu bidirectional for alle edges i grafen, eksempelvis har $e_1$ en edge til $e_3$ i $M_R$, og $e_3$ har en edge til $e_1$ i $M^T_{R}$. Unionen af disse gør denne edgen mellem de vertices bidirectional.

\subsection[]{Now let $T$ be the transitive closure of the relation $S$. What is the matrix representation of $T$? 
Can you explain in words what the relation $T$ is by describing how it can be interpreted?
}



\subsection[]{Suppose that we instead let $T^\prime$ be the transitive closure of the relation $R$, and then let
$S^\prime$ be the symmetric closure of $T^\prime$. Are $S^\prime$ and $T$ the same relation? If they are not the
same, show some way in which they differ. If they are the same, is it true that $S^\prime$ and $T$
constructed in this way from some relation $R$ on a set $A$ will always be the same? Please
make sure to motivate your answers clearly.
}



\section[Question 5]{Recall that an undirected graph $G = (V, E)$ consists of a set of vertices $V$ connected by
edges $E$, where every edge is an unordered pair of vertices. If there is an edge $(u, v)$ between two
vertices $u$ and $v$, then we say that $u$ and $v$ are the endpoints of the edge, and the two vertices are
said to be neighbours. We say that a sequence of edges $(v_1, v_2), (v_2, v_3), (v_3, v_4), \ldots, (v_{k-1}, v_k)$,
in $E$ is a path from $v_1$ to $v_k$. In this problem, we wish to express properties of graphs in both natural language and pred-
icate logic, and to translate between the two forms. We do this as follows:
\begin{itemize}
\item The universe is the set of vertices $V$ of $G$.
\item The binary predicate $E(u, v)$ holds if and only if there is an edge between $u$ and $v$ in $G$.
\item The unary predicate $S(v)$ is used to identify a subset of vertices $S = \{v \mid v \in V, S(v) \text{ is true}\}$
for which some property might or might not hold.
\end{itemize}
For example, we can write the natural language statement "$S$ is a set containing exactly $k$ distinct
elements" as a formula
\[\text{setsize}(S, k) := \exists u_1 \cdots \exists u_k \left(\bigwedge_{i=1}^{k-1} \bigwedge_{j=i+1}^{k} (u_i \neq u_j) \wedge \bigwedge_{i=1}^{k} S(u_i) \right)\]
\[\wedge \neg \exists u_1 \cdots \exists u_{k+1} \left(\bigwedge_{i=1}^{k} \bigwedge_{j=i+1}^{k+1} (u_i \neq u_j) \wedge \bigwedge_{i=1}^{k} S(u_i) \right) \tag{1}\]
where $\bigwedge_{i=1}^{k} \phi_i$ is shorthand for $\phi_1 \wedge \phi_2 \wedge \cdots \wedge \phi_k$, and where we use standard notation $\neg$ for
logical negation. In natural language, this formula can be read as: "There exist $k$ elements $u_1$ to
$u_k$ such that (i) for every pair $(u_i, u_j), i \neq j$, the elements themselves are also distinct $(u_i \neq u_j)$;
and (ii) all the $u_i$ for $i = 1, \ldots, k$ are members of $S$, but no such set of $k+1$ elements $u_1$ to $u_{k+1}$
exists."
Below you find six graph properties defined in natural language and six graph properties
written as predicate logic formulas. Most of the natural language definitions have equivalent
predicate logic formulas, but not all.
Your task is to translate each predicate logic formula (a), $\ldots$, (f) into a natural language
description, and argue which—if any—of the natural language definitions (1), $\ldots$, (6) it matches.\\
\n
\textbf{Natural Language Definitions:}\\
\n
(1) A \emph{dominating set} of size $k$ for a graph $G = (V, E)$ is a set $S$ of $k$ distinct vertices such that every vertex $v$ in the graph either is in $S$ or is a neighbour of a vertex in $S$.\\
\n
(2) A \emph{clique} $S$ of size $k$ in a graph $G = (V, E)$ is a set $S$ of $k$ distinct vertices such that all vertices in $S$ are neighbours with each other.\\
\n
(3) A \emph{disconnected vertex set} of size $k$ in a graph $G = (V, E)$ is a set $S$ of $k$ distinct vertices such that there are no edges from any $u \in S$ to any $v \in V \setminus S$. [Here $V \setminus S$ denotes set subtraction, so that $V \setminus S = \{v \mid v \in V \text{ and } v \not\in S\}$.]\\
\n
(4) A \emph{vertex cover} of size $k$ of a graph $G = (V, E)$ is a set $S$ of $k$ distinct vertices such that for every edge $(u, v) \in E$ it holds that at least one of the endpoints is in $S$.\\
\n
(5) A graph $G = (V, E)$ is \emph{bipartite}, with one of the parts in the bipartition having size $k$, if there a set $S$ of $k$ distinct vertices such that all edges in the graph go between $S$ and $V \setminus S$.\\
\n
(6) A \emph{connected component} $S$ of size $k$ in a graph $G = (V, E)$ is a set $S$ of $k$ distinct vertices such that for every pair of distinct vertices $u$ and $v$ in $S$ there is a path from $u$ to $v$ consisting of vertices in $S$.\\
\n
\textbf{Predicate Logic Formulas:}\\
\n
(a) $setsize(S, k) \wedge \forall v \forall w \left(E(v, w) \rightarrow S(v) \vee S(w)\right)$\\
\n
(b) $setsize(S, k) \wedge \forall v \left(S(v) \vee \exists w(S(w) \wedge E(v, w))\right)$\\
\n
(c) $setsize(S, k) \wedge \forall u \forall w\left((u \neq w \wedge S(u) \wedge S(w)) \rightarrow \exists v(E(u, v) \wedge E(v, w))\right)$\\
\n
(d) $setsize(S, k) \wedge \forall v \forall w\left(E(v, w) \rightarrow ((S(v) \wedge \neg S(w)) \vee (\neg S(v) \wedge S(w)))\right)$\\
\n
(e) $setsize(S, k) \wedge \forall v\left(S(v) \rightarrow \exists w(\neg S(w) \wedge E(v, w))\right)$\\
\n
(f) $setsize(S, k) \wedge \forall v \forall w\left((v \neq w \wedge S(v) \wedge S(w)) \rightarrow E(v, w)\right)$\\
\n
For every predicate logic formula that matches a natural language description, explain clearly why there is a match. For formulas that do not match a description, write a natural language definition along the lines of (1), \ldots, (6) that describes the property that the formula encodes.}


\subsection{Predicate Logic Formulas}
Vi oversætter først formlerne, hvorefter vi finder den bedst passende beskrivelse til dem.\\

(a) Et sæt $S$ af en graf $G=(V,E)$ bestående af $k$ unikke vertices, hvor mindst en af alle de vetices der danner en edge med i $S$.\\

(b) Et sæt $S$ af en graf $G=(V,E)$ bestående af $k$ unikke vertices, hvor enhver vertex i grafen enten selv er i $S$ eller er nabo til mindst en vertex i $S$.\\

(c) Et sæt $S$ af en graf $G=(V,E)$ bestående af $k$ unikke vertices, hvor for ethvert par af forskellige vertices $u,w \in S$ findes der en vertex $v$ i grafen, som er forbundet direkte til både $u$ og $w$.\\

(d) Et sæt $S$ af en graf $G=(V,E)$ bestående af $k$ unikke vertices, hvor for enhver edge $(v,w) \in E$ gælder det, at præcis et af vertices'ne er i $S$ (altså enten $v \in S$ og $w \notin S$, eller $v \notin S$ og $w \in S$). Dette beskriver en bipartition graf, hvor $S$ udgør den ene del af opdelingen.\\

(e) Et sæt $S$ af en graf $G=(V,E)$ bestående af $k$ unikke vertices, hvor enhver vertex $v \in S$ har mindst en edge med en vertex $w$ som ikke er i $S$.\\

(f) Et sæt $S$ af en graf $G=(V,E)$ bestående af $k$ unikke vertices, hvor alle vetices har en edge med en vertex, som ikke er sig selv.\\

\subsection{Natural Language Definitions}
(a) = ?\\
(b) = beskrivelse 1





\end{document}